Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-11-05 forecast/paper/pnas-suppl-template.tex
Add medRXiv submission doc; fix Addison's middle initial
add proper DOIs to forecast supplement

\author{Daniel J.\ McDonald, Jacob Bien, Alden Green, Addison Hu, Nat DeFries, Sangwon Hyun, Natalia L.\ Oliveira, James Sharpnack, Jingjing Tang, Robert Tibshirani, Valerie Ventura, Larry Wasserman, and Ryan J.\ Tibshirani}
\correspondingauthor{Daniel J. McDonald.\\E-mail: daniel@stat.ubc.ca}

@@

>>>>

\author{Daniel J. McDonald, Jacob Bien, Alden Green, Addison J. Hu, Nat DeFries,
  Sangwon Hyun, Natalia L. Oliveira, James Sharpnack, Jingjing Tang, Robert
  Tibshirani, Valerie Ventura, Larry Wasserman, and Ryan J. Tibshirani} 
\correspondingauthor{Daniel J. McDonald.\\E-mail: daniel@stat.ubc.ca}

@@

\FloatBarrier

\dataset{Code}{Code for reproducibility. {\tt R} script files and small
  datasets. 
  Persistent DOI: \url{https://doi.org/10.5281/zenodo.5639567}}

\dataset{Data}{Large intermediate data sets. Archived {\tt .RDS} (R objects)
  files 
  containing all evaluations for forecasting and hotspots using vintage and
  finalized data. Can be used to produce the graphics and conclusions in the
  manuscript without rerunning the entire pipeline. 
  Persistent DOI: \url{https://doi.org/10.5683/SP3/UW4VTC}}

### 2021-11-05 forecast/paper/supplement.tex
add proper DOIs to forecast supplement

\dataset{predictions.zip}{Archived {\tt .RDS} (R objects) files containing
  all predictions for forecasting and hotspots using vintage and finalized data.
Persistent DOI to be added at publication.}

\dataset{evaluations.zip}{Archived {\tt .RDS} (R objects) files containing
  all evaluations for forecasting and hotspots using vintage and finalized data.
  Persistent DOI to be added at publication.}

\dataset{analysis.zip}{Archived {\tt .RDS} (R objects) files containing
  additional data used to produce graphics and conclusions in the manuscript.
  Persistent DOI to be added at publication.}

\dataset{code.zip}{R script files containing
  all code used to reproduce the analysis described in the manuscript.
  Persistent DOI to be added at publication.}

>>>>

\dataset{Code}{Code for reproducibility. {\tt R} script files and small
  datasets. 
  Persistent DOI: \url{https://doi.org/10.5281/zenodo.5639567}}

\dataset{Data}{Large intermediate data sets. Archived {\tt .RDS} (R objects)
  files 
  containing all evaluations for forecasting and hotspots using vintage and
  finalized data. Can be used to produce the graphics and conclusions in the
  manuscript without rerunning the entire pipeline. 
  Persistent DOI: \url{https://doi.org/10.5683/SP3/UW4VTC}}
